### 2025-09-14 download-football-data.qmd
20250914 - NFL trades

#nfl_trades_raw <- progressr::with_progress(
#  nflreadr::load_trades(seasons = TRUE))

nfl_trades_raw <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/trades.csv")
```

>>>>

nfl_trades_raw <- progressr::with_progress(
  nflreadr::load_trades(seasons = TRUE))

#nfl_trades_raw <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/trades.csv")
```
